Comparing Power Optimizations in the Reorder Buffer

### 2011-06-10 paper/end.tex
Describe items in tables to start results section.

@@

For all instruction streams, we note that while the circular ROB powered 17,936 bits pe cycle (bit-cycles / cycles), the distributed ROB powered 27,692 bits per cycle. This is largely due to the presence of the central FIFO queue, which must keep a set of pointers to the location of actual entries in the ROB components of each functional unit. The extra cost of this is offset by shorter bit-lines and word-select lines, which as previously mentioned are not currently tabulated.

>>>>

Cycles measure the number of cycles a particular ROB implementation takes from getting the first instruction from issue to committing the last instruction in the stream. Bit-cycles denote total number of bits in the ROB that are powered for one cycle. E.g., a 20-bit buffer running for 8 cycles yields a measurement of 160 bit-cycles. We implement buffers that trade off execution time and extra bits for power savings in various ways, and bit-cycles, once plugged into a energy model system, provides a good measure of how much leakage power will be consumed. Transition to high is self-descriptive, and is included in the table as a measure of dynamic power dissipation. Register comparators estimate the number of times comparators are used to on register addresses and head/tail pointers.

@@

For all instruction streams, we note that while the circular ROB powered 17,936 bits pe cycle (bit-cycles / cycles), the distributed ROB powered 27,692 bits per cycle. This is due to the presence of the central FIFO queue, which must keep a set of pointers to the location of actual entries in the ROB components of each functional unit. The basic circular buffer requires 70 bits per entry. For the FIFO queue, 37 extra bits are required for each entry in each ROB component, an increase of 53\%.
The extra cost of this is offset by shorter bit-lines and word-select lines, which as previously mentioned are not currently tabulated.
